GPU-based Adaptive Beamforming for Active Sonar Imaging

### 2012-05-08 ECUA2012/gpu_capon_ecua2012.tex
la2pdf commit - 2012:05:08	02:22:49	(Tue 8.May)

The \gls{MVDR} beamformer is an algorithm well suited for implementation on a \gls{GPU}. Each pixels in the image can be processed independently, and the various steps within each pixel .

In a sonar processing chain, using one or more \glspl{GPU} can help offload the CPU.

We achieved speedups Our \gls{GPU} implementation 
Using \glspl{GPU} to accelerate the is a

>>>>

The \gls{MVDR} beamformer is an algorithm well suited for implementation on a \gls{GPU}. This is because the computations are independent on a pixel level, and partially also within each pixel. We were able to achieve speedup factors of 2-3 orders of magnitude by implementing our active sonar capable \gls{MVDR} implementation on a high-end \gls{GPU}. In sonar processing chains where the \gls{CPU} strain is considerable, simply being able to offloading some computationally intensive tasks to an idling \gls{GPU} might be just what is needed.
